\documentclass[10.8 pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry,enumitem}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage{multicol}
\usepackage{fontawesome}

\newcommand{\corrauthor}{\textsuperscript{*}}
\newcommand{\paperlink}[1]{\href{#1}{\,\small\faExternalLink}}

\def\name{Xiting Zhuang}

\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{margin=1in}
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}
\setlength\parindent{0em}

\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
	\end{list}
}

\begin{document}
	
	{\huge \textbf{\name}}
	
	\vspace{0.25in}
	
 

\noindent
\begin{minipage}[t]{0.50\textwidth}
	\faEnvelope\ \href{mailto:xiting.zhuang@ndsu.edu}{xiting.zhuang@ndsu.edu} \\
	\faGlobe\ \href{https://xiting-zhuang.github.io}{xiting-zhuang.github.io}
\end{minipage}\hfill
\begin{minipage}[t]{0.47\textwidth}
	\raggedleft
	North Dakota State University \\
	Richard H. Barry Hall 438 \\
	Fargo, ND 58102
\end{minipage}

	
	% =====================
	\section*{\textbf{Professional Experience}}
	
	\begin{itemize}
		
		\item[-]  Research Assistant Professor \hfill Nov 2024 – Present \\
		North Dakota State University   \hfill Fargo, ND  
		
		\item[-]  Postdoctoral Research Associate  \hfill Feb 2024 – Oct 2024 \\
		Texas A\&M University \hfill College Station, TX
		
	\end{itemize}
	
	% =====================
	\section*{\textbf{Education}}
	\begin{itemize}
		\item[-] University of Connecticut, Department of Agricultural \& Resource Economics \hfill Storrs, CT \\
		Ph.D. in Agricultural and Resource Economics  \hfill 2024
		
		\item[-] Fuzhou University, School of Economics \& Management \hfill Fuzhou, China \\
		M.S. in Quantitative Economics \hfill 2017
		
		\item[-] Georgia Institute of Technology, College of Computing \hfill Atlanta, GA \\
		M.S. in Computer Science (current)
		
		\item[-] Xiamen University, Tan Kah Kee College \hfill Xiamen, China \\
		B.A. in Accounting \hfill 2014
	\end{itemize}
	
	% =====================
	\section*{\textbf{Research}}
	
	\subsection*{\textbf{Peer-Reviewed Publications}}
	\begin{itemize}
		
		\item[-] Zhiyong Dai, Weidong Tian, Minglin Wang, \& \textbf{Xiting Zhuang\corrauthor}. The call of kinship: How clan culture shapes rural residents' commitment to hometown development in China. \emph{\textit{Journal of Rural Studies} (Accepted)}.
				
				
		\item[-] Peng Lu\corrauthor, Lulu Mao, \textbf{Xiting Zhuang}, Zhihong Xu, \& Shuai Ma (2026). U.S. public perceptions of food date labeling: Text mining and content analysis of USDA request for information (RFI) responses. \textit{Food Policy}, 140, 103055.\paperlink{https://www.sciencedirect.com/science/article/abs/pii/S0306919226000229}
		
		\item[-] Zhihong Xu\corrauthor, Shuai Ma, \textbf{Xiting Zhuang}, Anjorin Ezekiel Adeyemi, \& Ashlynn Kogut (2026). 
		Machine learning-assisted abstract screening on learning analytics: A step-by-step tutorial. 
		\textit{Systematic Reviews}, 15, 103.\paperlink{https://doi.org/10.1186/s13643-026-03111-2}
		
		\item[-] Weidong Tian, Zhiyong Dai, Dongli Cao, \& \textbf{Xiting Zhuang\corrauthor} (2025). Parental educational pairings and child physical abuse: Evidence from China. \textit{International Journal of Educational Development}.\paperlink{https://doi.org/10.1016/j.ijedudev.2025.103449}
		
		\item[-] Weidong Tian, Dongli Cao, \& \textbf{Xiting Zhuang\corrauthor} (2025). Work environment and intimate partner violence against women: Evidence from China. \textit{Applied Economics}.\paperlink{https://doi.org/10.1080/00036846.2025.2590113}
		
		\item[-] Zhihong Xu\corrauthor, \textbf{Xiting Zhuang}, \& Shuai Ma (2025). Machine learning-assisted systematic review: A case study in learning analytics. \textit{Education Sciences}, 15(11), 1488.\paperlink{https://doi.org/10.3390/educsci15111488}
		
		\item[-] Colin A. Carter, Sandro Steinbach\corrauthor, \& \textbf{Xiting Zhuang} (2025). The 2021 container shipping crisis and its consequences for US agricultural exports. \textit{Journal of Transport Economics and Policy}, 59(2), 110--136.\paperlink{https://www.ingentaconnect.com/contentone/lse/jtep/2025/00000059/00000002/art00004}
		
		\item[-] Sandro Steinbach\corrauthor \& \textbf{Xiting Zhuang} (2025). Trade implications of ending China's zero-Covid policy. \textit{Asian Economics Letters}, 6(3), 11--22.\paperlink{https://doi.org/10.46557/001c.137226}
		
		\item[-] Sandro Steinbach\corrauthor \& \textbf{Xiting Zhuang} (2024). Global container shipping disruptions, pop-up ports, and U.S. agricultural exports. \textit{Applied Economic Perspectives and Policy}, 46(2), 553--571.\paperlink{https://doi.org/10.1002/aepp.13399}
		
		\item[-] Sandro Steinbach\corrauthor \& \textbf{Xiting Zhuang} (2023). The impact of maritime shipping disruptions on U.S. tree nut exports and inventories. \textit{Agribusiness}, 39(3), 904--911.\paperlink{https://doi.org/10.1002/agr.21809}
		
		\item[-] Sandro Steinbach\corrauthor \& \textbf{Xiting Zhuang} (2023). U.S. agricultural exports and the 2022 Mississippi River drought. \textit{Agribusiness}, 41(1), 289--303.\paperlink{https://doi.org/10.1002/agr.21880}
		
		\item[-] Colin A. Carter, Sandro Steinbach\corrauthor, \& \textbf{Xiting Zhuang} (2023). Supply chain disruptions and containerized agricultural exports from California ports. \textit{Applied Economic Perspectives and Policy}, 45(2), 1051--1071.\paperlink{https://doi.org/10.1002/aepp.13311}
		
		\item[-] Heidi Schweizer, Sandro Steinbach\corrauthor, \& \textbf{Xiting Zhuang} (2022). A portrait of firms that trade in meat products. \textit{Western Economics Forum}, 20(2), 6--18.\paperlink{https://doi.org/10.22004/ag.econ.329728}
		
		\item[-] Raghav Goyal, Sandro Steinbach, Yasin Yildirim, \& \textbf{Xiting Zhuang} (2024). U.S. agricultural trade challenges amid climate and geopolitical disruptions. \textit{Choices}, 39(3), 1--7.\paperlink{https://www.choicesmagazine.org/choices-magazine/submitted-articles/us-agricultural-trade-challenges-amid-climate-and-geopolitical-disruptions}
		
		\item[-] Sandro Steinbach\corrauthor \& \textbf{Xiting Zhuang} (2023). Retaliatory tariffs and container shipping disruptions cause considerable trade damages to California's almond industry. \textit{Choices}, 38(2).\paperlink{https://www.choicesmagazine.org/choices-magazine/submitted-articles/retaliatory-tariffs-and-container-shipping-disruptions-cause-considerable-trade-damages-to-californias-almond-industry}
		
		\item[-] \textbf{Xiting Zhuang\corrauthor} (2016). Urbanization process and carbon emission in China based on semi-parametric spatial lags model. \textit{Logistics Engineering and Management}.
	\end{itemize}
	
	
	\subsection*{\textbf{Working Papers}}
	\begin{itemize}
		
 		\item[-] \textbf{Xiting Zhuang\corrauthor}, Sandro Steinbach, \& Carlos Zurita. Tariff pass-through in the 2025 U.S.--China tariff increase.
 
 
		\item[-] Weidong Tian, Dongli Cao, \& \textbf{Xiting Zhuang\corrauthor}. Tradition or tragedy: Arranged marriages and domestic violence. \emph{\textbf{R\&R} at \textit{International Review of Law \& Economics}}.
		

		
		\item[-] Zhihong Xu, Jaehyun Ahn, Shuai Ma, Anjorin Ezekiel Adeyemi, Fahmida Husain Choudhury, \textbf{Xiting Zhuang}, Rafael Landaverde, \& Gary J. Wingenbach. Bridging language and data: Transforming agricultural curricula for data analytics through linguistic insights. \emph{\textbf{R\&R} at \textit{PLOS One}}.
		
		\item[-] Weidong Tian \& \textbf{Xiting Zhuang\corrauthor}. The gift of equality: Legal recognition of same-sex unions and elder abuse.  
		
 
		
		\item[-] \textbf{Xiting Zhuang\corrauthor}. Temperature, allowance, and air pollution: Evidence from regression discontinuity design.
		
		\item[-] Weidong Tian \& \textbf{Xiting Zhuang\corrauthor}. Bread and bruises: The Great Chinese Famine and domestic violence.
		
		\item[-] Sandro Steinbach \& \textbf{Xiting Zhuang\corrauthor}. Global supply chain and domestic cost shocks.
		
		\item[-] Sandro Steinbach \& \textbf{Xiting Zhuang\corrauthor}. Global trade effects of tightening environmental trade policies in China.
	\end{itemize}
	
	
	\subsection*{\textbf{Policy Briefs and Outreach Work}}
	\begin{itemize}
		
		\item[-] Shawn Arita, Ruchira Chakravorty, Jiyeon Kim, Wint Lwin, Sandro Steinbach, Ming Wang, \& \textbf{Xiting Zhuang} (2026). IEEPA fertilizer tariffs: Revenue, relief, and pass-through. \textit{NDSU Agricultural Trade Monitor 2026-01}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_df79f1f42b5f4d98a0428a2c43085b98.pdf}
		
		\item[-] Shawn Arita, Matthew Gammans, Jiyeon Kim, Wint Lwin, Sandro Steinbach, Ming Wang, \& \textbf{Xiting Zhuang} (2025). Supreme Court, food and input tariff relief, and market access opportunities through recent trade deals. \textit{NDSU Agricultural Trade Monitor 2025-12}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_c0952c30cd4848a7b76fead0aed0853e.pdf}
		
		\item[-] Shawn Arita, Jiyeon Kim, Wint Lwin, Sandro Steinbach, Ming Wang, \& \textbf{Xiting Zhuang} (2025). Implications of new U.S.-China deal, soybean commitments, port fee suspension, and SE Asia deals. \textit{NDSU Agricultural Trade Monitor 2025-11}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_26d85e314b884039ac6aa9f2d9b3b739.pdf}
		
		\item[-] Shawn Arita, Jiyeon Kim, Wint Lwin, Sandro Steinbach, Ming Wang, \& \textbf{Xiting Zhuang} (2025). China could bypass U.S. soybeans in 2025/26 and IEEPA tariffs raise input costs. \textit{NDSU Agricultural Trade Monitor 2025-10}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_8ba2525b1280446489c686bb8f45bef1.pdf}
		
		\item[-] Shawn Arita, Jiyeon Kim, Wint Lwin, Sandro Steinbach, \& \textbf{Xiting Zhuang} (2025). Soybean basis hits record low amid zero new-crop sales to China. \textit{NDSU Agricultural Trade Monitor 2025-09}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_a43f5e48de2d400f88da267c58abfc6f.pdf}
		
		\item[-] Shawn Arita, Jiyeon Kim, Wint Lwin, Sandro Steinbach, Ming Wang, \& \textbf{Xiting Zhuang} (2025). IEEPA tariff escalation: What it means for U.S. food and ag-input imports. \textit{NDSU Agricultural Trade Monitor 2025-08}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_44202bdfcc8f4c01af0995141c8215fe.pdf}
		
		\item[-] Shawn Arita, Sandro Steinbach, Ming Wang, \& \textbf{Xiting Zhuang} (2025). China's import declines reflect broader demand weakness. \textit{NDSU Agricultural Trade Monitor 2025-07}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_d4656ab5a23e4cb2a2d9572e4817be85.pdf}
		
		\item[-] Shawn Arita, Sandro Steinbach, \& \textbf{Xiting Zhuang} (2025). \textit{NDSU Agricultural Trade Monitor 2025-06}. Center for Agricultural Policy and Trade Studies, North Dakota State University.\paperlink{https://www.capts-ndsu.com/_files/ugd/3c6228_275669f200b147d6993ae2fef14c7edc.pdf}
		
		\item[-] Sunghun Lim, Sandro Steinbach, \& \textbf{Xiting Zhuang} (2024). Panama Canal traffic delays threaten Southern Ag global supply chains. \textit{Southern Ag Today}.\paperlink{https://southernagtoday.org/2024/01/18/panama-canal-traffic-delays-threaten-southern-ag-global-supply-chains/}
		
		\item[-] Sandro Steinbach, Yasin Yildirim, \& \textbf{Xiting Zhuang} (2024). Ripple effects of shipping lane disruptions on U.S. agriculture. \textit{Farmdoc Daily}.\paperlink{https://farmdocdaily.illinois.edu/2024/01/ripple-effects-of-shipping-lane-disruptions-on-u-s-agriculture.html}
		
		\item[-] Raghav Goyal, Sandro Steinbach, Yasin Yildirim, \& \textbf{Xiting Zhuang} (2024). Southern U.S. agriculture faces headwinds in Asia amid Red Sea shipping disruptions. \textit{Southern Ag Today}.\paperlink{https://southernagtoday.org/2024/02/01/southern-u-s-agriculture-faces-headwinds-in-asia-amid-red-sea-shipping-disruptions/}
		
		\item[-] Sandro Steinbach \& \textbf{Xiting Zhuang} (2023). Down the river: How the 2022 Mississippi River drought damaged Southern U.S. agricultural trade. \textit{Southern Ag Today}.\paperlink{https://southernagtoday.org/2023/05/04/down-the-river-how-the-2022-mississippi-river-drought-damaged/}
		\item[-] Heidi Schweizer, Sandro Steinbach, \& \textbf{Xiting Zhuang} (2022). International market concentration in the Southern meat trading market. \textit{Southern Ag Today}.\paperlink{https://southernagtoday.org/2022/07/14/international-market-concentration-in-the-southern-meat-trading-market/}
		
		\item[-] Sandro Steinbach \& \textbf{Xiting Zhuang} (2022). Shipping container disruptions cause considerable export losses for Southern ports. \textit{Southern Ag Today}.\paperlink{https://southernagtoday.org/2022/04/shipping-container-disruptions-cause-considerable-export-losses-for-southern-ports/}
		
		\item[-] Sandro Steinbach \& \textbf{Xiting Zhuang} (2021). Cost-benefit analysis of detection systems for protecting critical infrastructure from UAV threats in Connecticut. \textit{Eversource Energy}.
		\item[-] Colin A. Carter, Sandro Steinbach, \& \textbf{Xiting Zhuang} (2021). Containergeddon and California agriculture. \textit{ARE Update}, 25(2), 1--4.\paperlink{https://giannini.ucop.edu/publications/are-update/issues/2021/25/2/containergeddon-and-california-agriculture/}
	\end{itemize}
	
	
	\begin{footnotesize}
		\textit{Note: Entries marked with \textsuperscript{*} denote Xiting Zhuang as the corresponding author.}
	\end{footnotesize}
	
	
	% =====================
	\section*{\textbf{Grants and Funding}}
	
	\begin{itemize}
		\item[-] \textbf{USDA National Institute of Food and Agriculture (NIFA)} \hfill \textit{Submitted October 2025} \\
		\textit{Partnership: Next Generation Trade Intelligence for U.S. Beef, Pork, and Poultry Producers} \\
		\textbf{Role: Co–Principal Investigator (Co–PI)} \\
		Total Budget: \$800,000 \hfill (NDSU Subaward: \$275,000) \\
		\textbf{Project Director (PD):} Modhurima Amin, Texas Tech University \\
		\textbf{Performance Period:} 09/01/2026 – 08/31/2029 \\
	\end{itemize}
	
	
	% =====================
	\section*{\textbf{Teaching Experience}}
	\begin{itemize}
		\item[-] North Dakota State University \hfill Fargo, ND \\
		\textbf{Guest Lecturer}, Econ 472/672 – International Trade \hfill Spring 2025
		
		\item[-] University of Connecticut \hfill Storrs, CT \\
		\textbf{Teaching Assistant}, ARE 3250 – Business Management \hfill Spring 2020
		
		\item[-] University of Connecticut \hfill Storrs, CT \\
		\textbf{Teaching Assistant}, ARE 2210/SARE 460 – Essentials of Accounting and Business \hfill Fall 2019
	\end{itemize}

	% =====================
	\section*{\textbf{Service on Graduate Student Committees}}
	\begin{itemize}
		\item[-] Benjamin Donkor (Ph.D. Student), Agricultural and Biosystems Engineering, NDSU \hfill Current
		\item[-] Laurent Sessi (M.S. Student), Agribusiness and Applied Economics, NDSU \hfill Current
	\end{itemize}

	% =====================
	\section*{\textbf{Conference Invited Talks}}
	
	\begin{itemize}
		\item[-] International Agricultural Trade Research Consortium (IATRC) \hfill Washington, DC \\
		``Tariff Pass-Through in the 2025 U.S.–China Tariff Escalation.'' \hfill Dec 2025  
		
		\item[-] Agricultural \& Applied Economics Association (AAEA) Annual Meeting \hfill New Orleans, LA \\
		``Temperature, Allowance, and Air Pollution: Evidence from Regression Discontinuity Design.'' \hfill Jul 2024  
		
		\item[-] International Agricultural Trade Research Consortium (IATRC) \hfill Clearwater, FL \\
		``Global Supply Chain and Trade Cost Shocks.'' \hfill Dec 2023  
		
		\item[-] Agricultural \& Applied Economics Association (AAEA) Annual Meeting \hfill Washington, DC \\
		``U.S. Agricultural Exports and the 2022 Mississippi River Drought.'' \hfill Jul 2023  
		
		\item[-] AAEA at ASSA \hfill New Orleans, LA \\
		``Global Container Trade Disruptions, Pop-Up Ports, and U.S. Agricultural Exports.'' \hfill Jan 2023  
		
		\item[-] International Agricultural Trade Research Consortium (IATRC) \hfill Clearwater, FL \\
		``Covid-19 Pandemic on International Trade: Evidence from China.'' \hfill Dec 2022  
		
		\item[-] Agricultural \& Applied Economics Association (AAEA) Annual Meeting \hfill Anaheim, CA \\
		``Global Shipping Container Disruptions and U.S. Agricultural Exports.'' \hfill Aug 2022  
		
		\item[-] Northeastern Agricultural \& Resource Economics Association (NAREA) Meeting \hfill Mystic, CT \\
		``Supply Chain Crisis and Empty Shipping Containers.'' \hfill Jun 2022  
		
		\item[-] CAHNR Graduate Student Research Forum, University of Connecticut \hfill Storrs, CT \\
		``Global Trade Effects of Tightening Environmental Standards in China.'' \hfill May 2022  
		
		\item[-] Steinbach Research Group Seminar, University of Connecticut \hfill Storrs, CT \\
		``Global Shipping Container Disruptions and U.S. Agricultural Exports.'' \hfill Mar 2022  
		
		\item[-] International Agricultural Trade Research Consortium (IATRC) \hfill Virtual \\
		``The Heterogeneous Effect of Vaccination on Trade in the United States.'' \hfill Jan 2021  
		
		\item[-] Association of Environmental \& Resource Economists (AERE) Summer Conference \hfill Virtual \\
		``The Waste Backhaul Between the United States and China.'' \hfill Jun 2021  
		
		\item[-] European Association of Environmental \& Resource Economists (EAERE) \hfill Virtual \\
		``Environmental Standard, Waste Backhaul and Maritime Trade.'' \hfill Jun 2021  
		
		\item[-] Northeastern Agricultural \& Resource Economics Association (NAREA) Annual Meeting \hfill Mystic, CT \\
		``Global Waste Crisis? The Role of Chinese Environmental Trade Policies.'' \hfill Jul 2020  
		
		\item[-] Association of Environmental \& Resource Economists (AERE) Summer Conference \hfill Virtual \\
		``International Trade Effects of Stricter Environmental Trade Policies in China.'' \hfill Jun 2020  
		
		\item[-] Agricultural \& Applied Economics Association (AAEA) Annual Meeting \hfill Atlanta, GA \\
		``Global Trade Effects of Tightening Environmental Standards in China.'' \hfill Jul 2019  
		
		\item[-] Agricultural \& Resource Economics Seminar, University of Connecticut \hfill Storrs, CT \\
		``Global Trade Effects of Tightening Environmental Standards in China.'' \hfill Oct 2019  
		
	\end{itemize}
	
	
	\section*{\textbf{Conference Presentations (Coauthored)}}
	
	\begin{itemize}
		
		\item[-] Western Region American Association for Agricultural Education \hfill San Marcos, TX \\
		``Bridging Language and Data: Transforming Agricultural Curricula for Big Data Analytics Through Linguistic Insights.'' \hfill Sep 2025
		
		\item[-] Association for International Agricultural and Extension Education (AIAEE) \hfill Inverness, Scotland \\
		``Evaluating ChatGPT for Abstract Screening in Systematic Reviews: A Case Study on the Beef Production Risk.'' \hfill Apr 2025
		
	\end{itemize}
	
	
	% =====================
	\section*{\textbf{Referee Service}}
	\begin{itemize}
		\item[-] Agribusiness
		\item[-] Violence Against Women
		\item[-] Humanities and Social Sciences Communications
		\item[-] Applied Economic Perspectives and Policy
		\item[-] Oxford Bulletin of Economics and Statistics
		\item[-] International Food and Agribusiness Management Review
		\item[-] Journal of the Agricultural and Applied Economics Association
		\item[-] Agricultural \& Applied Economics Association (Conference Review)
	\end{itemize}
	
	% =====================
	\section*{\textbf{Honors, Awards, \& Fellowships}}
	\begin{itemize}
		\item[-] Conference Participation Award, Graduate School, University of Connecticut \hfill 2022
		\item[-] 26th Participation Grant, European Association of Environmental and Resource Economists \hfill 2021
		\item[-] Predoctoral Fellowship Award, ARE, University of Connecticut \hfill 2021
		\item[-] Summer Fellowship, ARE, University of Connecticut \hfill 2020
		\item[-] 2019 Travel Award, Agricultural \& Applied Economics Association  \hfill 2019
		\item[-] Summer Fellowship, ARE Department, University of Connecticut \hfill 2019
		\item[-] TKK First Order Scholarship, Xiamen University \hfill 2011
	\end{itemize}
	
	
	% =====================
	\section*{\textbf{Affiliations}}
	\begin{itemize}
		\item[-] Agricultural and Applied Economics Association
		\item[-] International Agricultural Trade Research Consortium
		\item[-] Northeastern Agricultural and Resource Economics Association
		\item[-] Association of Environmental and Resource Economists
		\item[-] European Association of Environmental and Resource Economists
	\end{itemize}
	
	% =====================
	\section*{\textbf{Miscellaneous}}
	\begin{itemize}
		
		\item[-] \textit{Computational Skills:} Python, machine learning, text mining, API-based data collection, R, Stata, SQL, \LaTeX, ArcGIS, Git
		
		\item[-] \textit{Languages:} English (Professional proficiency), Mandarin Chinese (Native), Hokkien (Native)
		
	\end{itemize}
	
	% =====================
	\newpage
	% =====================
	\section*{\textbf{References}}
	
	\begin{multicols}{2}
		\begin{enumerate}[leftmargin=0in]
			
			\item[] Sandro Steinbach, Associate Professor \\
			Department of Agricultural and Resource Economics \\
			North Dakota State University \\
			\href{mailto:sandro.steinbach@ndsu.edu}{sandro.steinbach@ndsu.edu}
			
			\item[] Emma Bojinova, Associate Professor in Residence \\
			Department of Agricultural and Resource Economics \\
			University of Connecticut \\
			\href{mailto:emma.bojinova@uconn.edu}{emma.bojinova@uconn.edu}
			
			\item[] Siew Hoon Lim, Professor \\
			Department of Agribusiness and Applied Economics \\
			North Dakota State University \\
			\href{mailto:Siew.Lim@ndsu.edu}{Siew.Lim@ndsu.edu}
			
			\item[] Colin A. Carter, Distinguished Professor \\
			Department of Agricultural and Resource Economics \\
			University of California, Davis \\
			\href{mailto:cacarter@ucdavis.edu}{cacarter@ucdavis.edu}
			
		\end{enumerate}
	\end{multicols}
	
	
	\vfill
	\begin{center}
		\begin{footnotesize}
			\raggedleft Last updated: \today
		\end{footnotesize}
	\end{center}
	
\end{document}