% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10.5 pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry,enumitem}
\usepackage[T1]{fontenc}


 


% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
% \usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
% \usepackage[T1]{fontenc} 
 %\usepackage[osf]{xagaramon}
  %\usepackage{eulervm}

 
\usepackage{xcolor}

% Set your name here
\def\name{Xiting Zhuang}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/cv}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdfkeywords = {economics, econometrics, industrial organization,
		applied microeconomics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	margin=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
	\end{list}
}

\begin{document}
	
	% Place name at left
	{\huge \textbf{\name}}
	
	% Alternatively, print name centered and bold:
	%\centerline{\huge \bf \name}
	
	\vspace{0.25in}
	
	\begin{minipage}[t]{0.45\textwidth}
		Doctoral Candidate \\
		Phone: +1 (786) 239-0840 \\
		Email: \href{mailto:xiting.zhuang@uconn.edu}{xiting.zhuang@uconn.edu} \\
		Website: \href{https://xiting-zhuang.github.io}{xiting-zhuang.github.io} \\
		
	\end{minipage}
	\begin{minipage}[t]{0.6\textwidth}
		\href{https://uconn.edu/}{University of Connecticut} \\
		\href{https://are.uconn.edu/}{Department of Agricultural and Resource Economics} \\
		1376 Storrs Road,  	\\
		Storrs CT 06269-4023 
	\end{minipage}
	
	
		\section*{\textbf{Fields of Interest}}
	
	Causal Inference, International Trade and Policy,  Supply Chains 
	
	
	\section*{\textbf{ Education}}
	\begin{itemize}
		\item[-]  University of Connecticut, Department of Agricultural \& Resource Economics  \hfill Storrs, CT \\
	 Doctor of Philosophy, Agricultural and Resource Economics  \hfill  Feb, 2024  
	
			
			Committee:	 	 Sandro Steinbach,	Emma Bojinova, and Charles Towe 
			
			Thesis Title: ``\textit{Agri-Food Trade in Times of Global Supply Chain Disruptions}''
 
		 
	
		 \item[-]    Georgia Institute of Technology, College of  Computing \hfill   Atlanta, GA   \\ 
		 Master of Science, Computer Science  \hfill      2024  
 
	Specialization: Machine Learning
 
	%	\end{itemize}
		\item[-]  Fuzhou University, School of Economics \& Management \hfill Fuzhou, China \\ 
		Master of Science,   Quantitative Economics  \hfill    2017
		
 
		\item[-]  Xiamen University, Tan Kah Kee College    \hfill  Xiamen, China \\
		Bachelor of Art,  Accounting \hfill    2014
 
	\end{itemize}
	
 
 
 \section*{\textbf{ Professional Experience}}
 \begin{itemize}
 	\item[-]  Texas A\&M University, Texas A\&M AgriLife Research  \hfill College Station, TX \\
 	Postdoctoral Research Associate   \hfill  Mar  2024  - Current
 	
 	  
 	
 	\item[-]    University of Connecticut, Department of Computer Science \& Engineering \hfill   Storrs, CT   \\  Graduate Research Assistant, with Prof. Dr. Caiwen Ding  \hfill    Aug 2023 - Jan 2024 
 	  
 	
 	\item[-]  Eversource Energy Center \hfill Storrs, CT   \\ 
 	Graduate Research Assistant   \hfill    Jan 2019- Oct 2020
 	
 	
  	\item[-]    University of Connecticut, Department of Agricultural \& Resource Economics \hfill   Storrs, CT   \\  Graduate Research Assistant, with Prof. Dr. Sandro Steinbach  \hfill      Sep 2018 - Jan 2024
 

 
 
 \end{itemize}
 
 
	\section*{\textbf{Research  Affiliations}}
	
 
		North Dakota State University 
	\begin{itemize}
		\item[-] Department of Agribusiness and Applied Economics, Research Affiliate	\hfill    2023\,--\,  Present
	\end{itemize}
 
	 
 
	
	\section*{\textbf{Research}}
	
		\subsection*{\textbf{Publications}}
		
		\begin{itemize}
 
 
 
 
  	 \item[-]   Steinbach, S.,  \&  \underline{Zhuang, X.} (2023). Global Container Shipping Disruptions, Pop-Up Ports, and U.S. Agricultural Exports. \textit{\textbf{Applied Economic Perspectives and Policy}}. 1-19.  
 \href{http://doi.org/10.1002/aepp.13399}{[{\underline{\textcolor{blue}{link}}}]}
 
  	 \item[-]   Steinbach, S.,  \&  \underline{Zhuang, X.} (2023).  The Impact of Maritime Shipping Disruptions on U.S. Tree Nut Exports and Inventories.   \textit{\textbf{Agribusiness}}. 
 \href{https://doi.org/10.1002/agr.21809}{[{\underline{\textcolor{blue}{link}}}]}
 
 
 
  	 \item[-]   Steinbach, S.,  \&  \underline{Zhuang, X.} (2023).   U.S. Agricultural Exports and the 2022 Mississippi River Drought.  \textit{\textbf{Agribusiness}}. 	\href{https://ageconsearch.umn.edu/record/335476/files/26473.pdf}{[{\underline{\textcolor{blue}{link}}}]}
 
 
 
  	 \item[-]   Steinbach, S.,  \&  \underline{Zhuang, X.} (2023).  Retaliatory Tariffs and Container Shipping Disruptions Cause Considerable Trade Damages to California’s Almond Industry.'',  \textit{\textbf{Choice}}. 38(2) 	\href{https://econpapers.repec.org/scripts/redir.pf?u=https%3A%2F%2Fageconsearch.umn.edu%2Frecord%2F337188%2Ffiles%2FSteinbach_Retaliatory_38.pdf;h=repec:ags:aaeach:337188}{[{\underline{\textcolor{blue}{link}}}]}
 
 


   	 \item[-]   Carter Colin A., Steinbach, S.,  \&  \underline{Zhuang, X.} (2022). ``Supply chain disruptions and containerized agricultural exports from California ports.'', \textit{\textbf{Applied Economic Perspectives and Policy}}. 
 \href{https://doi.org/10.1002/aepp.13311}{[{\underline{\textcolor{blue}{link}}}]}
 

   	 \item[-]   Schweizer, H., Steinbach, S.,  \&  \underline{Zhuang, X.} (2022).  A Portrait of Firms that Trade in Meat Products. \textit{\textbf{Western Economics Forum}}.   \href{https://waeaonline.org/wp-content/uploads/2022/12/WEF-Fall-2022-Issue-20-Volume-2-All-Intro-and-Articles.pdf#page=6}{[{\underline{\textcolor{blue}{link}}}]}
 
 
      \item[-] Carter, Colin A., Sandro Steinbach, and \underline{Xiting Zhuang}.. ```Containergeddon’ and California Agriculture.'' \textit{ARE Update} 25(2): 1–4. University of California Giannini Foundation of Agricultural, University of California, Davis. 2021 \href{https://s.giannini.ucop.edu/uploads/pub/2021/12/20/v25n2_1.pdf}{[{\underline{\textcolor{blue}{link}}}]}
		 	
		 \item[-]	\underline{Xiting, Zhuang}. ``Urbanization Process and Carbon Emission in China Based on Semi-Parametric Spatial Lags Model.'',   \textit{Logistics Engineering and Management}. 2016. 
	%	\href{http://www.cnki.com.cn/Article/CJFDTotal-SPCY201702047.htm}{\texttt{http://www.cnki.com.cn/Article/CJFDTotal-SPCY201702047.htm}} 
 

 	
 
		\end{itemize}
	
 
		
		
		
		
	\subsection*{\textbf{Working Papers}}
	
	\begin{itemize}
	

\item[-]	``Global Supply Chain and Trade Cost Shocks.''  
\href{https://xiting-zhuang.github.io/file/jmp.pdf}{[{\underline{\textcolor{blue}{Link}}}]}  




	 \item[-]	``Global Shipping Container Disruptions and U.S. Agricultural Exports.'',  with Colin Carter, and Sandro Steinbach.  (Under review)
	  	\href{http://dx.doi.org/10.22004/ag.econ.320397}{[{\underline{\textcolor{blue}{link}}}]}
	
	
 
 

 
	
 		
	 \item[-] ``Global Trade Effects of Tightening Environmental Trade Policies in China.'', with Sandro Steinbach. 
\href{https://www.dropbox.com/scl/fi/21o4ldsv04zo4w7bs6y5w/Manuscript.pdf?rlkey=phzrh7uhti8zm0wxpn786gu94&dl=0}{[{\underline{\textcolor{blue}{link}}}]}

 

	\end{itemize}
	
 
 \subsection*{\textbf{ Work in Progress}}
 
 \begin{itemize}
 
 	
 	\item[-] ``After Maths of the Basel Convention: The Trade Effects of Environmental Provisions in Preferential Trade Agreements.''
 	 	
 	
 	\item[-] ``Environmental Standard, Waste Backhaul and Maritime Trade.'',
 	with Sandro Steinbach. 
 	\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=gSddLM4AAAAJ&citation_for_view=gSddLM4AAAAJ:9yKSN-GCB0IC}{[{\underline{\textcolor{blue}{link}}}]}
 	
 
 	
 	\item[-] ``The Role of Clientele Politics on Agricultural Subsidies.'',
 	with
 	\href{https://are.uconn.edu/person/sandro-steinbach/}{Sandro Steinbach}.   
 	

 	
 	

 	
 \end{itemize}
 

\subsection*{\textbf{Policy Briefs and Outreach Work}}

\begin{itemize}
	
	\item[-]  Goyal R., Steinbach, S., Yildirim Y. \& \underline{Zhuang, X.} (2024). ``Southern U.S. Agriculture Faces Headwinds in Asia Amid Red Sea Shipping Disruptions.'' \textit{\textbf{Southern Ag Today}}, 4(4.4).
\href{https://southernagtoday.org/2024/01/25/southern-u-s-agriculture-faces-headwinds-in-asia-amid-red-sea-shipping-disruptions/}{[{\underline{\textcolor{blue}{link}}}]} 



	
	\item[-] Steinbach, S., \& \underline{Zhuang, X.} (2023). ``Down the River: How the 2022 Mississippi River Drought Damaged Southern U.S. Agricultural Trade.'' \textit{\textbf{Southern Ag Today}}, 2(4.5).
	\href{https://southernagtoday.org/2023/05/04/down-the-river-how-the-2022-mississippi-river-drought-damaged/}{[{\underline{\textcolor{blue}{link}}}]} 
	
	\item[-] Schweizer, H., Steinbach, S., \& \underline{Zhuang, X.} (2022). ``International Market Concentration in the Southern Meat Trading Market.'' \textit{\textbf{Southern Ag Today}}, 2(29.4).
	\href{https://southernagtoday.org/2022/07/international-market-concentration-in-the-southern-meat-trading-market/}{[{\underline{\textcolor{blue}{link}}}]} 
	
	\item[-] Steinbach, S., \& \underline{Zhuang, X.} (2022). ``Shipping Container Disruptions Cause Considerable Export Losses for Southern Ports.'' \textit{\textbf{Southern Ag Today}}, 2(17.4).
	\href{https://southernagtoday.org/2022/04/shipping-container-disruptions-cause-considerable-export-losses-for-southern-ports/}{[{\underline{\textcolor{blue}{link}}}]} 
	
	\item[-] Steinbach, S., \& \underline{Zhuang, X.} (2021). ``Cost-Benefit Analysis of Detection Systems for Protecting Critical Infrastructure from UAV Threats in Connecticut,'' \textit{\textbf{Eversource Energy}}.
	\href{https://www.dropbox.com/s/hmnrb6rljgsyvei/UConn%20CBA%20Report%202021.pdf?dl=0}{[{\underline{\textcolor{blue}{link}}}]} 
	
	
\end{itemize}



 \subsection*{\textbf{Selected Media Coverage}}
 
\begin{itemize}
	
		
\item[-] ``US Is Losing Soybean-Export Edge as Brazil Closes Logistics Gap,'' \textit{Bloomberg}, September 6, 2022.     \\	\href{https://www.bloomberg.com/news/articles/2022-09-06/us-losing-soybean-export-edge-as-brazil-closes-logistics-gap?leadSource=uverify%20wall}{\texttt{https://www.bloomberg.com/news/articles/2022-09-06/}}



	\item[-] ``US Citrus Growers Struggle During Supply Chain Snarl,'' \textit{The Epoch Times}, February 16, 2022.     \\	\href{https://www.theepochtimes.com/u-s-citrus-growers-struggle-during-supply-chain-snarl_4283693.html}{\texttt{https://www.theepochtimes.com/}}
	
	
	
	
	\item[-] ``Assembly Select Committee on Ports and Goods Movement,'' \textit{California State Assembly	Committee on Agriculture}, February 2, 2022.     \\	\href{https://www.assembly.ca.gov/sites/assembly.ca.gov/files/ag_export_briefing_document_final.pdf}{\texttt{https://www.assembly.ca.gov/}}
	
	
	
	\item[-] ````Containergeddon'' Results in \$2.1B Loss to California Farmers,'' \textit{Western Growers}, January 20, 2022.     \\	\href{https://www.wga.com/blog/“containergeddon”-results-21b-loss-california-farmers}{\texttt{https://www.wga.com/blog/“containergeddon”}}
	
	
	\item[-] ``Containergeddon Cost Ag \$2.1 Billion Last Summer, And Supply Chain Bottlenecks Aren’t Over Yet.'', KVPR, NPR \textit{for Central California}, January 11, 2022.     \\  
	\href{https://kvpr.org/business-economy/2022-01-11/containergeddon-cost-ag-2- 1-billion-last-summer-and-supply-chain-bottlenecks-arent-over-yet}{\texttt{https://kvpr.org/business-economy/2022-01-11}}
	
	
	
	
		
	\item[-] ``Inefficient California Ports Cost Farmers Billions.'', \textit{UConn Today}, January 3, 2022.     \\	\href{https://today.uconn.edu/2022/01/inefficient-california-ports-cost-farmers-billions/}{\texttt{https://today.uconn.edu/2022/01/}}
	
	
	
	

	
	
\end{itemize}
 
 
 
 
		
 \subsection*{\textbf{Extramural Funding}}
		
\begin{itemize}

\item[-]  National Institute of Food and Agriculture, AFRI Program: ``\textit{Workshop on Transforming Agricultural Global Value Chains},'' (USD 50,000): assisted PI (S. Steinbach) with grant proposal writing, including reference and content editing. 
			
\item [-] National Institute of Food and Agriculture, AFRI Program: “Evaluating the Impact of Preferential Trade Agreements on Agricultural and Food Trade: New Insights from Natural Language Processing and Machine Learning,”  (USD 650,000): assisted PI (S. Steinbach) with grant proposal preparation, coordinated literature review for objectives 1 and 2, edited references and constructed workplan. 
			
\item [-] National Institute of Food and Agriculture, EWD Program: “Measuring the Impact of Foreign Trade Shocks on Agriculture in the United States,” (USD 180,000): assisted PI (D. Kim) with text editing, references, and career plan development. 
			
			
			
 
			
	\item[-] ``\textit{Theory and Application of Semi-Parametric Global Vector Auto Regression Model,}'' supported by the National Natural Science Foundation of China, Project No. 71571046. Supported and provided research assistance, 2014
				
	\item [-] ``\textit{Application and Theory of Semi-parametric Spatial Panel Data Simultaneous Equation Model,}'' supported by the Specialized Research Fund for the Doctoral Program of Higher Education of China (SRFDP), Project No. 20103514110009. Supported and provided research assistance, 2014
				
				
				
\end{itemize}
		
		
 
	
	


	
	
	
	%\begin{itemize}
	%\item Blevins, Jason~R. (forthcoming).
	%\href{http://jblevins.org/research/generic-list}%
	% {A Generic Linked List Implementation in Fortran 95}.
	%\textit{ACM SIGPLAN Fortran Forum}.
	%\end{itemize}
	
	\section*{\textbf{Invited Conference \& Seminar Presentations}}
	
	
	
	\begin{itemize}
		
			\item[-]	2023 International Agricultural Trade Research Consortium (IATRC)  \hfill Clearwater, FL\vspace{0.15cm} \\
``Global Supply Chain and Trade Cost Shocks'' \hfill   Dec, 2023


		\item[-]	2023 Agricultural \& Applied Economics  Association Annual Meeting (AAEA)   \hfill   Washington DC\vspace{0.15cm} \\
``U.S. Agricultural Exports and the 2022 Mississippi River Drought''  \hfill Jul, 2023



   \item[-]  2023 AAEA at ASSA    \hfill   New Orleans, LA\vspace{0.15cm} \\
	``Global Container Trade Disruptions, Pop-Up Ports, and U.S. Agricultural Exports''  \hfill Jan, 2023 

 

			\item[-]	2022  International Agricultural Trade Research Consortium (IATRC)   \hfill Clearwater, FL\vspace{0.15cm} \\
	``Covid-19 Pandemic on International Trade: Evidence from China'' \hfill   Dec, 2022
	
	
		\item[-]	2022  Agricultural \& Applied Economics  Association Annual Meeting (AAEA)   \hfill   Anaheim, CA\vspace{0.15cm} \\
			``Global Shipping Container Disruptions and U.S. Agricultural Exports''   \hfill   Aug, 2022
			
		\item[-]  2022 Northeastern Agricultural and Resource Economics Association   Meeting (NAREA)   \hfill   Mystic, CT\vspace{0.15cm} \\
		 	``Supply Chain Crisis and Empty Shipping Containers'' \hfill Jun, 2022  
			
		\item[-] 	2022 Spring, CAHNR Graduate Student Research Forum,  UConn \hfill Storrs, CT\vspace{0.15cm} \\ 
			``Global Trade Effects of Tightening Environmental Standards in China'' \hfill   May, 2022 
			
					\item[-] 	Steinbach Research Group Seminar, UConn \hfill Storrs, CT\vspace{0.15cm} \\
			``Global Shipping Container Disruptions and U.S. Agricultural Exports'' \hfill   Mar, 2022
			
		\item[-]	2021  International Agricultural Trade Research Consortium (IATRC) \hfill  Virtual\vspace{0.15cm}      \\
			``The heterogeneous effect of vaccination on trade in the United States'' \hfill   Jan, 2021 
		
		\item[-]  	2021  Association of Environmental \& Resource Economists Summer Meeting (AERE) \hfill  Virtual\vspace{0.15cm}  \\
		``The Waste Backhaul Between the United States and China'' \hfill   Jun, 2021 
		\item[-]  2021 European Association of Environmental \& Resource Economists (EAERE) \hfill  Virtual\vspace{0.15cm}  \\
		``Environmental Standard, Waste Backhaul and Maritime Trade'' \hfill  Jun, 2021 
		 
		\item[-] 2020  Northeastern Agricultural \& Resource Economics Annual Meeting (NAREA)    \hfill Mystic, CT \vspace{0.15cm} \\
				``Global Waste Crisis? The Role of Chinese Environmental Trade Policies'' \hfill  Jul, 2020 
		\item[-] 2020  Association of Environmental \& Resource Economists  Summer Meeting (AERE)  \hfill  Virtual\vspace{0.15cm} \\
				``International Trade Effects of Stricter Environmental Trade Policies in China'' \hfill   Jun, 2020 
		\item[-] 2019 Agricultural \& Applied Economics Association  Annual Meeting (AAEA) \hfill Atlanta, GA\vspace{0.15cm} \\
				``Global Trade Effects of Tightening Environmental Standards in China''  \hfill Jul, 2019
		
		\item[-] 2019  Agricultural \& Resource Economics Seminar, University of Connecticut    \hfill  Storrs, CT\vspace{0.15cm} \\
				``Global Trade Effects of Tightening Environmental Standards in China''  \hfill Oct, 2019
	\end{itemize}	
	
	
	
	\section*{\textbf{Journal/Conference Referee}}
	
	\begin{itemize}
		\item[-]  Oxford Bulletin of Economics and Statistics
		\item[-]  International Food and Agribusiness Management Review
		\item[-] Journal of the Agricultural and Applied Economics Association
		\item[-]  Agricultural \& Applied Economics Association
	\end{itemize}
	
	\section*{\textbf{Honors, Awards, \& Fellowships}}
	
	\begin{itemize}
		\item[-] Conference Participation Award, Graduate School, University of Connecticut, 2022
		\item[-] 26th EAERE Participation Grant, EAERE 2021
		\item[-] 2020-2021 Predoctoral Fellowship Award, ARE Department, University of Connecticut
		\item[-]  Summer  Fellowship, ARE Department, University of Connecticut, 2020
		\item[-] AAEA Travel Award, AAEA, 2019
		\item[-]  Summer  Fellowship, ARE Department, University of Connecticut, 2019
		\item[-] Xiamen University, TKK First Order Scholarship, 2011
		
	\end{itemize}
	
	
		\section*{\textbf{Affiliations}}
	\begin{itemize}
		% \item \textit{Security Clearance:} Special Sworn Status, U.S. Census Bureau.
		\item[-] Agricultural and Applied Economics Association
		\item[-] International Agricultural Trade Research Consortium
		\item[-] Northeastern Agricultural and Resource Economics Association
		\item[-] Association of Environmental and Resource Economists
		\item[-] European Association of Environmental and Resource Economists
		
	\end{itemize}
	
	
	
	\section*{\textbf{Miscellaneous}}
	\begin{itemize}
		% \item \textit{Security Clearance:} Special Sworn Status, U.S. Census Bureau.
		\item[-] \textit{Computer Skills:} ArcGIS, \LaTeX, Stata, SQL, Python,   Java, R
		\item[-] \textit{Languages:}  English (Professional),  Mandarin Chinese (Native), Hokkien (Native)
		
	\end{itemize}
	
	
	
	
	\newpage
	
	\section*{\textbf{References}}
	
	\begin{enumerate}[leftmargin=0in]
		\item[] Sandro Steinbach, Associate Professor  \\
		Department of Agricultural and Resource Economics \\
		North Dakota State University \\
				\href{mailto:sandro.steinbach@ndsu.edu}{\texttt{sandro.steinbach@ndsu.edu}}
				
		\item[] Emma Bojinova, Associate Professor in Residence \\
Department of Agricultural and Resource Economics \\
University of Connecticut \\
\href{mailto:emma.bojinova@uconn.edu}{\texttt{emma.bojinova@uconn.edu}}

		
 
 
 \item[] Charles Towe, Associate Professor \\
Department of Agricultural and Resource Economics \\
University of Connecticut \\
 \href{mailto:charles.towe@uconn.edu}{\texttt{charles.towe@uconn.edu}}
 
		

				\item[] Colin A. Carter, Distinguished Professor \\
		Department of Agricultural and Resource Economics \\
		University of California, Davis \\
				\href{mailto:cacarter@ucdavis.edu}{\texttt{cacarter@ucdavis.edu}}
		
		
	\end{enumerate}
\vfill
			
	\bigskip
	\bigskip 
	% Footer
	\begin{center}
		\begin{footnotesize}
		\raggedleft	Last updated: \today \\
		\end{footnotesize}
	\end{center}
	
\end{document}